---
title: "week4"
author: "Leonardo Schneider"
date: "2025-07-02"
output: html_document
---


```{r}

library(dplyr)
library(stringr)
library(readr)
netflix_titles <- read_csv("netflix_titles.csv")
View(netflix_titles)
```
 
# Cleaning the data

```{r}

netflix_clean <- netflix_titles %>%
  filter(!is.na(type), !is.na(title), !is.na(listed_in), !is.na(date_added), !is.na(director), !is.na(country)) %>%
  mutate(
    type = str_trim(type),
    listed_in = str_trim(listed_in),
    country = str_trim(country)
  )

```

# Counting the documentaries 

```{r}
documentaries_unique <- netflix_clean %>%
  filter(str_detect(listed_in, "Documentaries")) %>%
  distinct(title)

nrow(documentaries_unique)

```

# Release year of the movies

```{r}
type_year <- netflix_clean %>%
  count(release_year, type)

library(ggplot2)
ggplot(type_year %>% filter(release_year >= 2010),
       aes(x = release_year, y = n, fill = type)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Netflix Releases by Year and Type",
    x = "Release Year",
    y = "Number of Titles",
    fill = "Type"
  ) +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2010, max(type_year$release_year, na.rm = TRUE), by = 1)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```


```{r}
library(tidyr)

genres <- netflix_clean %>%
  separate_rows(listed_in, sep = ", ") %>%
  count(listed_in, sort = TRUE)
```
# Top 5 Genres
## International movies are on the top

```{r}

top5_genres <- genres %>%
  top_n(5, n) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))


ggplot(top5_genres, aes(x = "", y = n, fill = listed_in)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  geom_text(aes(label = paste0(percentage, "%")),
            position = position_stack(vjust = 0.5), size = 4) +
  labs(
    title = "Top 5 Netflix Genres (by Frequency)",
    fill = "Genre"
  ) +
  theme_void()

```

# Top 10 countries with most netflix titles
## Of course US has the most movies followed by India that is the two biggest countries on the MOVIE world. My Country Brazil is ranked as #21.

```{r}
countries <- netflix_clean %>%
  separate_rows(country, sep = ", ") %>%
  count(country, sort = TRUE)

top_countries <- countries %>%
  top_n(10, n)
ggplot(top_countries, aes(x = reorder(country, n), y = n)) +
  geom_bar(stat = "identity", fill = "darkred") +
  coord_flip() +
  labs(
    title = "Top 10 Countries with Most Netflix Titles",
    x = "Country",
    y = "Number of Titles"
  ) +
  theme_minimal()



```


```{r}
countries %>%
  mutate(rank = row_number()) %>%
  filter(country == "Brazil")
```

# Top 10 Most Frequent Actors on Netflix.
## We are so used to watch movies and series from the western world that I was expecting to see more of those names showing up on the screen but India has a big influence on that and Samuel L Jackson was the only one that I truly knew from the list.

```{r}
top_cast <- netflix_clean %>%
  filter(!is.na(cast)) %>%
  separate_rows(cast, sep = ", ") %>%
  count(cast, sort = TRUE)


top_cast %>%
  slice_max(n, n = 10) %>%
  ggplot(aes(x = reorder(cast, n), y = n)) +
  geom_bar(stat = "identity", fill = "coral") +
  coord_flip() +
  labs(
    title = "Top 10 Most Frequent Actors on Netflix",
    x = "Actor/Actress",
    y = "Number of Titles"
  ) +
  theme_minimal()

```
# Top 10 US Most Frequent Actors on Netflix.
## Because I do not knew any of the other 9 actors in the top 10 I decided to go for the top 10 in US. The names are pretty known and I do not believe had any surprise. Older people had more movies in their life time of course.

```{r}
top_us_cast <- netflix_clean %>%
  filter(!is.na(cast), str_detect(country, "United States")) %>%
  separate_rows(cast, sep = ", ") %>%
  count(cast, sort = TRUE)

top_us_cast %>%
  slice_max(n, n = 10) %>%
  ggplot(aes(x = reorder(cast, n), y = n)) +
  geom_bar(stat = "identity", fill = "darkgreen") +
  coord_flip() +
  labs(
    title = "Top 10 US Most Frequent Actors on Netflix",
    x = "Actor/Actress",
    y = "Number of Titles"
  ) +
  theme_minimal()

```

